The Role of Video Data Sharing in Advancing Education Policy and Practice

### 2015-04-30 2015-06-01-nsf-ed-workshop/paper.tex
add nsf ed workshop

%https://www.overleaf.com/2636873dcbhqd#/6964401/
\documentclass[a4paper,man,natbib]{apa6}

@@

\title{Your APA6-Style Manuscript}
\shorttitle{Your APA6-Style Manuscript}
\author{You}
\affiliation{Somewhere}

@@

\section{Some \LaTeX{} Examples}
\label{sec:examples}

@@

LaTeX automatically generates a bibliography in the APA style from your .bib file. The citep command generates a formatted citation in parentheses \citep{Lamport1986}. The cite command generates one without parentheses. LaTeX was first discovered by \cite{Lamport1986}.

@@

Use the table and tabular commands for basic tables --- see Table~\ref{tab:widgets}, for example. You can upload a figure (JPEG, PNG or PDF) using the files menu. To include it in your document, use the includegraphics command as in the code for Figure~\ref{fig:frog} below.

% Commands to include a figure:
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{frog.jpg}
\caption{\label{fig:frog}This is a figure caption.}
\end{figure}

\begin{table}
\centering
\begin{tabular}{l|r}
Item & Quantity \\\hline
Widgets & 42 \\
Gadgets & 13
\end{tabular}
\caption{\label{tab:widgets}An example table.}
\end{table}

\subsection{Mathematics}

\LaTeX{} is great at typesetting mathematics. Let $X_1, X_2, \ldots, X_n$ be a sequence of independent and identically distributed random variables with $\text{E}[X_i] = \mu$ and $\text{Var}[X_i] = \sigma^2 < \infty$, and let
$$S_n = \frac{X_1 + X_2 + \cdots + X_n}{n}
      = \frac{1}{n}\sum_{i}^{n} X_i$$
denote their mean. Then as $n$ approaches infinity, the random variables $\sqrt{n}(S_n - \mu)$ converge in distribution to a normal $\mathcal{N}(0, \sigma^2)$.

@@

%
% Please see the package documentation for more information
% on the APA6 document class:
%
% http://www.ctan.org/pkg/apa6
%

>>>>

\documentclass[a4paper,man,natbib]{apa6}

@@

\title{The Role of Video Data Sharing in Advancing Education Policy and Practice}
\shorttitle{Video Data Sharing in Education}
\author{Rick O. Gilmore}
\affiliation{The Databrary (databrary.org) Project \\ \& The Pennsylvania State University}

@@

\section{Promise of Video Data Sharing}
\label{sec:examples}

@@

@@

@@
